---
name: Cynthia Huang
email:  cynthia.huang@monash.edu
phone: +61 411 238 243
www: cynthiahqy.com
format: cv-pdf
---

```{r}
#| include: false
library(tidyverse)
```

# SKILLS

## Programming

* Command line shell scripting (bash, zsh)
* Data analysis and modelling (R, python, MATLAB, SAS)
* Version control (git)
* Typesetting (LaTeX, markdown, quarto)

## Languages

* English *Native*
* Mandarin *Skilled*
* Cantonese *Skilled*
* Japanese *Basic*

# EDUCATION

**Doctor of Philosophy – Econometrics and Business Statistics**, *Monash University*\hfill  Aug 2021 -– Present

* Researching principles and methods for data preparation with applications in economics, official
statistics, and satellite deep learning
* Monash Data Futures Institute PhD Top-Up Scholarship (2021-2024)
* Expected graduation date: Nov 2024

**Bachelor of Commerce (Honours) – Economics**, *The University of Melbourne*\hfill Feb 2016 -– Nov 2016

* Graduated with First Class Honours
* Completed research essay modelling information escrows for victims of domestic violence

**Bachelor of Commerce – Economics & Management**, *The University of Melbourne*\hfill Mar 2012 -– Oct 2014

* Graduated with First Class Honours, and inclusion on Dean’s Honours List

**Summer School: EC307 Development Economics**, *London School of Economics*\hfill Jul 2014 -– Aug 2014

* Final Result: A

**Victorian Certificate of Education**, *The Mac.Robertson Girls' High School*\hfill Feb 2009 –- Nov 2011

* Australian Tertiary Admission Rank (ATAR): 98.95

# Employment history

```{r employment, results='asis'}
tribble(
    ~Start, ~End, ~Position,
    1985, 1992, "\\textbf{Statistical consultant}, Department of Statistics, University of Melbourne",
    1993, 1994, "\\textbf{Lecturer}, Department of Statistics, University of Melbourne",
    1995, 1996, "\\textbf{Lecturer}, Department of Mathematics and Statistics, Monash University",
    1997, 1998, "\\textbf{Senior Lecturer}, Department of Mathematics and Statistics, Monash University",
    1998, 1998, "\\textbf{Visiting Professor}, Department of Statistics, Colorado State University",
    1998, 2000, "\\textbf{Senior Lecturer}, Department of Econometrics \\& Business Statistics, Monash University",
    2001, 2003, "\\textbf{Associate Professor}, Department of Econometrics \\& Business Statistics, Monash University",
    2002, 2002, "\\textbf{Visiting Senior Research Fellow}, Mathematical Sciences Institute, Australian National University",
    2003, NA, "\\textbf{Professor}, Department of Econometrics \\& Business Statistics, Monash University",
    2016, 2016, "\\textbf{KNAW Visiting Professor}, TU/Eindhoven, Netherlands",
  ) |>
  arrange(-Start) |>
  mutate(
    Start = as.character(Start),
    End = as.character(End),
    End = replace_na(End, ""),
    Years = if_else(End == Start,
        as.character(Start),
        paste(Start, "--", End, sep = ""),
        paste(Start, "--", End, sep = "")
    )
  ) |>
  select(Years, Position) |>
  knitr::kable(escape=FALSE, bottomrule = '', toprule = '', midrule = '',
    col.names = NULL, booktab = TRUE)  |>
  kableExtra::kable_styling(full_width = FALSE, position = "left")
```
